E4-analysis-calibration

### 2024-08-22 group-d/E4-analysis-calibration.Rmd
little fixes to knit the pdf

```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x="Calibration Score", y="Bias Effect") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).

>>>>

```{r E4-calib-corr-plot, fig.cap= 'Calibration scores plotted against the verb bias effect (the difference in target animal fixations between modifier and instrument conditions).'}
ggplot(eyetracking.effects.by.subj, aes(x = mean_percent_in_roi, y = bias_effect))+
  geom_point()+
  geom_smooth(method = "lm") +
  labs(x="Calibration Score", y="Bias Effect") +
  theme_bw()+
  theme(panel.grid.minor = element_blank())
```
Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)`%). 
The quality of a participant's calibration significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ < 0.05).
The difference in target animal fixation proportions between modifier and instrument conditions was higher for participants with better calibration (see Figure \ \@ref(fig:E4-calib-corr-plot)).
